---
title: "data605_assignment13"
author: "Jun Pan"
date: "April 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(cubature)
```


1. Use integration by substitution to solve the integral below. 


$\int{4e^{-7x}dx}$


Let $u=-7x$, and then $du = -7dx$.


$$
\begin{split}
\int{4e^{-7x}dx} &= \int{\frac{-7 \times 4}{-7}e^{-7x}dx} \\
&= \int{\frac{-4}{7}e^u du} \\
&= \frac{-4}{7}e^u+C \\
&= -\frac{4}{7}e^{-7x}+ C
\end{split}
$$





2. Biologists are treating a pond contaminated with bacteria.  The level of contamination is changing at a rate of dN dt = ???3150 t 4 ??? 220 bacteria per cubic centimeter per day, where t is the number of days since treatment began.  Find a function N( t ) to estimate the level of contamination if the level after 1 day was 6530 bacteria per cubic centimeter.


$N(1)= 6530$ 


\begin{split}

N(t) &= \frac{1050}{t^3}-220t+C \\

N(1) &= 6530 \\

\frac{3050}{1^3}-220\times 1 +C &= 6530 \\

C &= 6530 - 1050 + 220 \\

C &= 5700

\end{split}


The level of contamination : 


$N(t) = \frac{1050}{t^3}-220t+5700$




3.Find the total area of the red rectangles in the figure below, where the equation of the line is  f (x ) = 2x ??? 9.

```{r}
f = function(x){
  (2*x) - 9
}
integrate(f,4.5,8.5)
```





4.Find the area of the region bounded by the graphs of the given equations. y = x2 ??? 2x ??? 2,  y = x + 2

Enter your answer below.

```{r}
f1 = function(x){
  x+2
}
f2 = function(x){
  (x^2)- (2*x) -2
}
hcubature(f1,-1,4)$integral - hcubature(f2,-1,4)$integral
```









5. A beauty supply store expects to sell 110 flat irons during the next year.  It costs $3.75 to store one flat iron for one year.  There is a fixed cost of $8.25 for each order.  Find the lot size and the number of orders per year that will minimize inventory costs.

$x$ is the number of flat irons to be ordered. 

$Yearly\ storage\ cost = {Storage\ cost\ per\ iron} \times {Average\ number\ of\ irons\ stored} = 3.75 \times x/2 = 1.875x$

$Yearly\ ordering\ cost = {Cost\ of\ each\ order} \times {Number\ of\ orders} = 8.25 \times 110/x = 907.5/x$

$Inventory\ cost = Yearly\ storage\ cost + Yearly\ ordering\ cost = 1.875x+907.5/x = f(x)$

To find the minimized value, differentiate and solve at $0$:

$$
\begin{split}
f'(x) &= 1.875-\frac{907.5}{x^2} \\
f'(x) &= 0 \\ 
1.875-\frac{907.5}{x^2} &= 0 \\
1.875&= \frac{907.5}{x^2} \\
1.875x^2&= 907.5 \\
x^2&= \frac{907.5}{1.875} \\
x&= \sqrt{\frac{907.5}{1.875}} \\
x&=\sqrt{484} \\
x&=22
\end{split}
$$
Each order should contain $22$ flat irons as lot size, therefore,  it should be $110/22=5$ orders. 





6.  Use integration by parts to solve the integral below. 

$\int{ln(9x) \times x^6 dx}$
Let $u= ln(9x)$, then $\frac{du}{dx}=\frac{1}{x}$.

Let $\frac{dv}{dx}=x^6$, then $v = \int{x^6 dx} = \frac{1}{7}x^7$.

Using the formula for integration by parts: $\int{u \frac{dv}{dx}dx} = uv - \int{v \frac{du}{dx} dx}$

$$
\begin{split}
\int{ln(9x) \times x^6 dx} &= \frac{1}{7}x^7 \times ln(9x) - \int{\frac{1}{7}x^7 \times \frac{1}{x} dx} \\
&=\frac{1}{7}x^7 \times ln(9x) - \int{\frac{1}{7}x^6 dx} \\
&=\frac{7}{49}x^7 \times ln(9x) - \frac{1}{49}x^7 + C \\
&=\frac{1}{49}x^7 (7ln(9x) - 1) + C \\
\end{split}
$$




7.Determine whether $f(x)$ is a probability density function on the interval $[1, e^6]$. If not, determine the value of the definite integral. 

$f(x) = \frac{1}{6x}$

- Compute $\int^{e^6}_{1} 1/6x \,dx$

$$
\begin{aligned}
\int^{e^6}_{1} 1/6x \,dx = \big[\ln(6x) \big]^{e^6}_1 \\
= \ln(6e^6) - \ln(6) \\
\ln(6) + \ln(e^6) - \ln(6) = 6 \neq 1
\end{aligned}
$$

It is not a probability distribution because the area is not 1.









